Reviving the Lost Art of Combinator Graph Reduction

### 2023-01-05 experiments/superg/doc/paper/paper.tex
Add a JIT placer.

@@

>>>>

The \texttt{call} instruction pushes the \texttt{EIP} register onto the stack, which contains the address of the 'instruction' after the \texttt{call}.
In our calling convention, this means the stack consists of pointers to the right-hand sides, very convenient.

A \texttt{push} instruction first decrements the stack pointer \texttt{rsp}, then writes the new value to the address of  \texttt{rsp}.
Assembly to load the value of the top of the stack is therefore: \texttt{mov rax, [rsp]}.
To load the second value: \texttt{mov rax, [rsp+8]}.

@@

Suggestion from \textit{Common Benchmarking Pitfalls}: Always look at your distribution.
When you have run benchmarks, take a look at the times for each sample.
